Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-12 paper.tex
Use publication format for PDF. Looks much nicer.
added Brunn reference

Bioclipse in turn acts as base for other software
such as Brunn~\cite{WebBrunn}, a laboratory information system for
microplate based high-throughput screening. Brunn provides a graphical interface
for handling different plate layouts and dilution series and can automaticly
generate dose response curves and calculate IC$_{50}$-values.

>>>>

Bioclipse in turn acts as base for other software
such as Brunn~\cite{Alvarsson:2011fk}, a laboratory information system for
microplate based high-throughput screening. Brunn provides a graphical interface
for handling different plate layouts and dilution series and can automaticly
generate dose response curves and calculate IC$_{50}$-values.
